---
title: "R&D"
author: "Hussain Alsalman"
date: "3/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tasi")
library("dplyr")
library("quantmod")
library("purrr")
library("PerformanceAnalytics")
library("highcharter")
library("lcyanalysis")
data("stock_indices")

```

## System requirements 
# 1 - Daily download of all data stock market
# 2 - Scan all data to identify trends  


# Information 
*primary trend* (timeframe : Years)
##Bull Trend 
It has three phases 
## Phase 1: 
reviving confidence from the prior primary bear market
## Phase 2: 
the second represents the response to increased corporate earnings
## Phase 3: 
third is when speculation becomes dominant and prices rise on “hopes and expectations.”

##Bear Trend 
It has three phases 
## Phase 1: 
abandonment of hopes upon which stocks were purchased
## Phase 2: 
selling due to decreased earnings
## Phase 3: 
distress selling, regardless of value, by those who believe the worst is yet to come or who are forced to liquidate

## Measuring Market Strength 
We can use advance decline line chart to determine the strength of a specific market 

```{r}
material_comp <-  stock_indices %>%
  filter(sectorName == "Materials") %>% 
  select(symbol,companyName) %>% 
  as.data.frame() 
```

```{r}
symbols <- material_comp[,1]
names(symbols) <-  material_comp[,2]
mat_prices <- data.frame()
stocks_list <- list()
for (i in 1:length(symbols)){
  stocks_list[[i]] <- getCompanyRecords(startDate = "2018-12-31",endDate = "2021-04-01",as.numeric(symbols[i]))
}
names(stocks_list) <- material_comp[, 2]
```

```{r}
# Convert to xts format
stocks_list_xts<-purrr::map(stocks_list, df_to_xts)
mrk_brdth<- stocks_list_xts %>%
  map(function(x) {x$change <- x$Close - x$Open;
                   x$ad <- ifelse(x$change > 0 , 1, -1)
                  return(x)})  %>% 
map(function(x) x$ad) %>% 
  pmap(sum) %>%
  flatten_dbl() %>% 
  cumsum() %>% 
  as.xts(order.by = index(stocks_list_xts[["Basic Chemical Industries Co."]]))
  
add_TA(mrk_brdth)
chart_Series(stocks_list_xts[["Basic Chemical Industries Co."]])
add_TA(downtrend(stocks_list_xts[["Basic Chemical Industries Co."]],day = 20,num = 2),on = TRUE, col = "red")
add_TA(uptrend(stocks_list_xts[["Basic Chemical Industries Co."]],day = 20,num = 2),on = TRUE, col = "green")


highchart(type = "stock") %>%
  hc_title(text = "Market breadth") %>%
     hc_yAxis_multiples(
    list(lineWidth = 3),
    list(showLastLabel = TRUE, opposite = TRUE)
  ) %>% 
  hc_add_series(mrk_brdth) %>% 
  hc_add_series(stocks_list_xts[["Basic Chemical Industries Co."]],yAxis = 1) %>% 
    hc_add_series(stocks_list_xts[["Takween Advanced Industries Co."]],yAxis = 1) %>% 
    hc_add_series(stocks_list_xts[["Saudi Kayan Petrochemical Co."]],yAxis = 1) %>% 
      hc_legend(
    align = "left",
    verticalAlign = "top",
    layout = "vertical",
    x = 0,
    y = 100
    )
    

```


# Select Random stocks for REITs
comps <- stock_indices %>%
  filter(sectorName == "Materials") %>% 
  select(symbol,companyName) %>% 
  as.data.frame() 


# Random sample of 5 Tickers & extracting their names
sample_n<- sample(1:dim(comps)[1],5)  
symbols <- comps[sample_n,1]
names(symbols) <-  comps[sample_n,2]

prices <- data.frame()
stocks_list <- list()
for (i in 1:length(symbols)){
  stocks_list[[i]] <- getCompanyRecords(startDate = "2018-12-31",endDate = "2021-03-22",as.numeric(symbols[i]))
}
# Retain the names of the tickers

strptime(Sys.time(), format = "yy")
#Convert them to xts 
stocks_list_xts<-purrr::map(stocks_list, df_to_xts)

monthly_prices <- stocks_list %>%
  map(df_to_xts) %>% 
  map(~Cl(.)) %>% 
  reduce(merge) %>% 
  na.omit() %>% 
  to.monthly(OHLC = FALSE, 
             indexAt = "lastof") 

asset_returns_xts <-
  Return.calculate(monthly_prices,
                   method = "log") %>%
  na.omit()
colnames(monthly_prices) <-  comps[sample_n, 2]  

ymam <- getCompanyRecords(startDate = "2020-01-01", endDate = "2021-03-22", 3020)
ymam_xts <- df_to_xts(ymam)
library("lcyanalysis")

quantmod::chart_Series(ymam_xts)
m_signals_riyad <- lcyanalysis::uptrend(ymam_xts, day = 20,num = 1)
quantmod::add_TA(x = m_signals_riyad, on = TRUE, col = "green")


highchart(type = "stock") %>%
  hc_title(text = "Monthly Log Returns") %>%
  hc_add_series(asset_returns_xts[, 1],
                name = comps[sample_n, 2][1]) %>%
  hc_add_series(asset_returns_xts[, 2],
                name = comps[sample_n, 2][2]) %>%
  hc_add_series(asset_returns_xts[, 3],
                name = comps[sample_n, 2][3]) %>%
  hc_add_series(asset_returns_xts[, 4],
                name = comps[sample_n, 2][4]) %>%
  hc_add_series(asset_returns_xts[, 5],
                name =  comps[sample_n, 2][5]) %>%
  hc_add_theme(hc_theme_flat()) %>%
  hc_navigator(enabled = FALSE) %>%
  hc_scrollbar(enabled = FALSE) %>%
  hc_exporting(enabled = TRUE) %>%
  hc_legend(enabled = TRUE)

w <- c(0.25,
       0.25,
       0.20,
       0.20,
       0.10)

portfolio_returns_xts_rebalanced_monthly <-
  Return.portfolio(asset_returns_xts,
                   weights = w,
                   rebalance_on = "months") %>%
  `colnames<-`("returns")

highchart(type = "stock") %>%
  hc_title(text = "Portfolio Monthly Returns") %>%
  hc_add_series(portfolio_returns_xts_rebalanced_monthly$returns,
                name = "Rebalanced Monthly",
                color = "cornflowerblue") %>%
  hc_add_theme(hc_theme_flat()) %>%
  hc_navigator(enabled = FALSE) %>%
  hc_scrollbar(enabled = FALSE) %>%
  hc_legend(enabled = TRUE) %>%
  hc_exporting(enabled = TRUE)

system.file("company_symbols","tasi")

